### 2024-11-28 CV2/papers.tex
update CV

\textbf{IntSGD: Adaptive floatless compression of stochastic gradients} (Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtarik). \textit{International Conference on Learning Representations}, 2022.

@@

\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Dmitry Kovalev, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized Finite-Sum Optimization over Time-Varying Networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Dmitry Kovalev, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov). \textit{arXiv preprint arXiv:2402.02490}, 2024.

>>>>

\textbf{\href{https://arxiv.org/abs/2102.08374}{IntSGD: Adaptive floatless compression of stochastic gradients}} (Konstantin Mishchenko, Bokun Wang, Dmitry Kovalev, Peter Richtarik). \textit{International Conference on Learning Representations}, 2022.

@@

\textbf{\href{https://arxiv.org/abs/2411.14601}{On Linear Convergence in Smooth Convex-Concave Bilinearly-Coupled Saddle-Point Optimization: Lower Bounds and Optimal Algorithms}} (Dmitry Kovalev, Ekaterina Borodich). \textit{arXiv preprint arXiv:2411.14601}, 2024.
\textbf{\href{https://arxiv.org/abs/2407.02020}{Decentralized Optimization with Coupled Constraints}} (Demyan Yarmoshik, Alexander Rogozin, Nikita Kiselev, Daniil Dorin, Alexander Gasnikov, Dmitry Kovalev). \textit{arXiv preprint arXiv:2407.02020}, 2024.

@@

\textbf{\href{https://arxiv.org/abs/2402.02490}{Decentralized finite-sum optimization over time-varying networks}} (Dmitry Metelev, Savelii Chezhegov, Alexander Rogozin, Aleksandr Beznosikov, Alexander Sholokhov, Alexander Gasnikov, Dmitry Kovalev). \textit{arXiv preprint arXiv:2402.02490}, 2024.
